Global adjoint tomography -- Model GLAD-M25

### 2018-12-04 main.tex
add plumes and subduction figures

%\begin{figure}[h]
%    \centering
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:b}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:c}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:d}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Canary_Iceland.png}\label{fig:e}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Hoggar_AFAR.png}\label{fig:f}}\\[-1pt]
%    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:g}}\\
%    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes near the AFAR region.}
%\end{figure}

@@

\subsection{Slabs}
\label{section:slabs}

@@

>>>>

\begin{figure}[h]
    \centering
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Afar.png}\label{fig:a}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Bermuda_Canary.png}\label{fig:b}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/CapeVerde_Hoggar.png}\label{fig:c}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Iceland_Eifel.png}\label{fig:d}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Easter_Galapagos.png}\label{fig:a}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/plumes/Marion3_Kerguelen.png}\label{fig:g}}\\
    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes.}
\end{figure}

@@

\subsection{Subduction Slabs}
\label{section:slabs}

@@

\begin{figure}[h]
    \centering
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Aeg.png}\label{fig:a}}\\[-4pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Br.png}\label{fig:b}}\\[-4pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Ha.png}\label{fig:c}}\\[-4pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Ne.png}\label{fig:d}}\\[-4pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Wc.png}\label{fig:a}}\\[-4pt]
    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes.}
\end{figure}
